### 2017-05-04 R/ITHIM.Rmd
ITHIM.Rmd is now running without error again

```{r statewiseGBD, eval = FALSE, dev=c('pdf', 'png'), fig.width = 2*fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = FALSE}
D <- melt(lapply(ITHIMList, function(ITHIM) return(ITHIM@parameters@GBD)))

D <- do.call(rbind,lapply(ITHIMList, getGBD))

names(D) <- c("disease","sex","ageClass","type", "burden", "sex2", "disease2", "state")

@@

deltaDALYList <- mapply(deltaBurden, ITHIMList, ITHIMListScenario)

## getDALY <- function( ITHIM ){
## foo <- data.frame(lapply(ITHIM@parameters@GBD, function(x) x$M$daly + x$F$daly))
## sum(foo[,names(foo) %in% c("BreastCancer","ColonCancer","Dementia","Depression","Diabetes", "CVD")])
## }

@@

>>>>

```{r statewiseGBD, eval = TRUE, dev=c('pdf', 'png'), fig.width = 2*fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = FALSE}
D <- do.call(rbind, mapply(function(df,state) data.frame(df, state = state), lapply(ITHIMList, getGBD), names(ITHIMList), SIMPLIFY = FALSE))
names(D) <- c("disease","sex","ageClass","type", "burden", "state")

@@

deltaDALYList <- mapply(deltaBurden, ITHIMList, ITHIMListScenario)
```

@@

```{r rustBeltOld, eval = FALSE, dev=c('pdf', 'png'), fig.width = 2*fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = FALSE}
## getDALY <- function( ITHIM ){
## foo <- data.frame(lapply(ITHIM@parameters@GBD, function(x) x$M$daly + x$F$daly))
## sum(foo[,names(foo) %in% c("BreastCancer","ColonCancer","Dementia","Depression","Diabetes", "CVD")])
## }

## cbPalette <- c("#0072B2", "#56B4E9", "#999999", "#E69F00", "#009E73", "#F0E442", "#D55E00", "#CC79A7")
